---
title: "First Knit"
author: "Briggette Adams"
date: "August 19, 2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I'm Confused")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting? 

I am sitting in the front of the class and I usually sit in the front in all my classes.I am sitting at computer #4. I do not like seat changes so I would have to give that a 1 because I like order. I can't say that I like teams but I don't mind them as long as everyone does their part. I have worked on a couple teams and they did not go well so I am too fond on them. 
  
   
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

I would like to be called by my name which is Briggette pronounced like bree-jhet.     
   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

In life I want to become a Mental Health Nurse for the US ARMY. My first major is in social and behavioral sciences. My second major is in nursing. College subjects that interest me are sciences classes either Bio science or psychology or sociology. I want to acheive my MA in Nursing.    
  
   
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

I have been to a few places in Mexico. I have never been in the military but I am a military spouse. If I was drafted I would want to go into the Army. The reason wehy is the fact that I am the daughter of a military family.     
  
   
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

Math 115 is a prerequisite of my nursing degree. In order to get into the masters program I would need to attain a B or better. I plan to get an A.   
  
   
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

I am somewhat knowledgeable of computers giving myself a 6-7. I currently have an apple Macbook Pro, I have internet access at home so I can complete all assignments. I drive to get to school everyday. Issues that limit the time I can be at school would be having a small child and working. I attended highschool at Highland High school in Palmdlae. I do have a have a job where I work full  time. 
  
   
  




